### 2017-02-28 num.tex
submitted_version
addressed comments by Csaba

 the error induced by the constraint approximation. The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}. We consider a single queue with arrivals and departures. The state of the system is the queue length with the state space given by $S=\{0,\ldots,n-1\}$, where $n-1$ is the buffer size of the queue. The action set $A=\{1,\ldots,d\}$ is related to the service rates. We let $s_t$ denote the state at time $t$. The state at time $t+1$ when action $a_t \in A $ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$. For states $s_t=0$ and $s_t=n-1$, the system dynamics is given by 	$s_{t+1}= s_{t}+1$ with probability $p$ when $s_t=0$ and $s_{t+1}=s_t-1$ with probability $q(a_t)$ when $s_t=n-1$. The service rates satisfy $0<q(1)\leq \ldots\leq q(d)<1$ with $q(d)>p$ so as to ensure `stabilizability' of the queue. The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s+60q(a)^3)$. We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}.

@@

The aggregation matrix $W_a$ is defined as below: for all $ i=1,\ldots,m$,

@@

(and intractable) sampler of \citep{CS}. \todoc{Right??}
We set $c(s)=(1-\zeta) \zeta^s$, where $s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively. The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$. Note that computing $\et$ was hard in the case of large $n=10^4$ and since $\et$ is completely dependent on the structure of $\Phi$, $T$ and $W$ we instead computed the same for $n=10$ and used it as a surrogate. Accordingly, we chose a smaller system $Q_S$ with $n=10$, $d=2$, $k=2$, $m=5$, $q(1)=0.2$, $q(2)=0.4$, $p=0.2$ and $\alpha=0.98$. Note that a better performance of $W_a$ and $W_c$ is in agreement with a lower value of $\et$.

@@

\begin{tabular}{|c|c|c|c|c|}\hline
Error Terms&	$W_i$&	$W_c$& $W_a$& $W_r$ \\\hline
$||J^*-\hj||_{1,c}$ for $\zeta=0.9$& $32$&	$32$& $220$& $5.04\times 10^4$ \\\hline
$||J^*-\hj||_{1,c}$ for $\zeta=0.999$& $110$&	$180.5608$& $82$& $1.25\times 10^7$ \\\hline
$\et$ & $0$&	$39$& $24$& $214$ \\\hline

@@

$||J_{\hu}||_{1,c}$ for $\zeta=0.9$& $-441.25$&	$-450.59$& $-446.49$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.999$& $-2.0611e+04$&	$-2.0611e+04$& $-2.0612e+04$ \\\hline

@@

\caption{Shows performance metrics for $Q_L$. Here $||J^*||_{1,c}=-439.26$ for $\zeta=0.9$ and $||J^*||_{1,c}=-2.0603e+04$ for $\zeta=0.999$   and a random policy yields a total reward of $-1.2661e+03

>>>>

 the error induced by the constraint approximation. The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}. We consider a single queue with arrivals and departures. The state of the system is the queue length with the state space given by $S=\{0,\ldots,n-1\}$, where $n-1$ is the buffer size of the queue. The action set $A=\{1,\ldots,d\}$ is related to the service rates. We let $s_t$ denote the state at time $t$. The state at time $t+1$ when action $a_t \in A $ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$. For states $s_t=0$ and $s_t=n-1$, the system dynamics is given by 	$s_{t+1}= s_{t}+1$ with probability $p$ when $s_t=0$ and $s_{t+1}=s_t-1$ with probability $q(a_t)$ when $s_t=n-1$. The service rates satisfy $0<q(1)\leq \ldots\leq q(d)<1$ with $q(d)>p$ so as to ensure `stabilizability' of the queue. The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s+60q(a)^3)$. We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work reasonably well for this domain \cite{ALP}.

@@

The aggregation matrix $W_a$ is defined as follows: for all $ i=1,\ldots,m$,

@@

(and intractable) sampler of \citep{CS}.
We set $c(s)=(1-\zeta) \zeta^s$, where $s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively. The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is close to that of the ideal sampler $W_i$. Note that computing $\et$ was hard in the case of large $n=10^4$ and since $\et$ is completely dependent on the structure of $\Phi$, $T$ and $W$ we instead computed the same for $n=10$ and used it as a surrogate. Accordingly, we chose a smaller system $Q_S$ with $n=10$, $d=2$, $k=2$, $m=5$, $q(1)=0.2$, $q(2)=0.4$, $p=0.2$ and $\alpha=0.98$. Note that a better performance of $W_a$ and $W_c$ is in agreement with a lower value of $\et$.

@@

\begin{tabular}{|c|c|c|c|c|c|}\hline
Queuing System&Error Terms&	$W_i$&	$W_c$& $W_a$& $W_r$ \\\hline
$Q_L$& $\norm{J^*-\hj}_{1,c}$ for $\zeta=0.9$& $32$&	$32$& $220$& $5.04\times 10^4$ \\\hline
$Q_L$& $\norm{J^*-\hj}_{1,c}$ for $\zeta=0.999$& $110$&	$180.5608$& $82$& $1.25\times 10^7$ \\\hline
$Q_s$& $\et$ & $0$&	$39$& $24$& $214$ \\\hline

@@

$\norm{J_{\hu}}_{1,c}$ for $\zeta=0.9$& $-441.25$&	$-450.59$& $-446.49$ \\\hline
$\norm{J_{\hu}}_{1,c}$ for $\zeta=0.999$& $-2.0611e+04$&	$-2.0611e+04$& $-2.0612e+04$ \\\hline

@@

\caption{Shows performance metrics for $Q_L$. Here $\norm{J^*}_{1,c}=-439.26$ for $\zeta=0.9$ and $\norm{J^*}_{1,c}=-2.0603e+04$ for $\zeta=0.999$   and a random policy yields a total reward of $-1.2661e+03
